---
title: "Full-Text Screening Reconciliation"
author: Emma Wilson
date: "12/11/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r project details, include=FALSE}
projectName <- "Systematic Review and Meta-Analysis of reporting on quality control standards and phenotypes of the basic cell model in brain cancer research: how reproducible is the field?" # Copied and pasted from SyRF
downloadDate <- "12 Nov 2020" # Date data was downloaded from SyRF
```

## Aims

This systematic review project utilised both title/abstract and full-text screening to identify relevant studies. The following code:

1. **Reads in** annotation from SyRF database
2. **Filters** relevant screening question
3. **Compares** Reviewer 1 and Reviewer 2 answers
4. **Outputs** file to reconcile disagreements

## 1. Load R Packages

```{r load libraries, message=FALSE}
library(dplyr)      # Data transformation
library(readr)      # Reads in data
library(tidyr)      # Pivot wider
```

## 2. Read in SyRF Data
Data are study level annotations only, from the SyRF project titled *`r projectName`* downloaded on `r downloadDate`.

```{r read data, message=FALSE}
# Study Level Annotations from SyRF Project
annotations_studyLevel <- read_csv(file = "data-raw/annotations_studyLevel_20201112.csv")
# All Studies from SyRF Project
studyInfo <- read_tsv(file = "data-raw/studyInfo.txt")
```


## 3. Tidy Data
Remove irrelevant columns from the dataset and pivot wider to allow each study screening answer to be compared.

```{r tidy data}
# Select Relevant Columns and Rename
dat <- annotations_studyLevel %>%
  rename(Relevance = "a1baa93f-6871-4806-816e-aad21f550876_Is this article relevant according to inclusion and exclusion criteria?",
         Reason = "05f8cae4-1a23-45d0-a11e-12f99c6afd9c_Why is the study not relevant?",
         Notes = "05f8cae4-1a23-45d0-a11e-12f99c6afd9c_Why is the study not relevant?_Notes") %>%
  select(StudyIdStr, Investigator, Relevance, Reason, Notes)

# Make Data Wider to Compare
screeningComparison <- dat %>%
  pivot_wider(names_from = Investigator,
              values_from = c("Relevance", "Reason", "Notes"))
```

## 4. Compare Full-Text Screening Answers
Create a new column to identify studies where two reviewers agreed or disagreed on whether a study was relevant based on full-text screening.

```{r compare}
# Mutate Column Using "ifelse"
screeningComparison <- screeningComparison %>%
  mutate(Relevance_Match = ifelse(Relevance_Timo == Relevance_joly, TRUE, FALSE)) %>%
  select(StudyIdStr, Relevance_Timo, Relevance_joly, Relevance_Match, Reason_Timo, Reason_joly, Notes_Timo, Notes_joly) # reorder the columns
```

```{r analyse, include=FALSE}
nTotal <- sum(nrow(screeningComparison)) # Total number of studies
nMatched <- sum(screeningComparison$Relevance_Match == TRUE) # Number of studies matching
nDifferent <- sum(screeningComparison$Relevance_Match == FALSE) # Number of studies with disagreement
```

Out of a **total `r nTotal` studies**, dual screened by two independent reviewers matched on **`r nMatched` studies** and disagreed on **`r nDifferent` studies**.

## 5. Output Data
Output the data in 3 formats:

**1. All studies**

```{r output human readable}
# Get titles and StudyIdStr
titles <- annotations_studyLevel %>%
  select(Title, StudyIdStr) %>%
  unique()

# Match on StudyIdStr
output <- merge(titles, screeningComparison, by = "StudyIdStr")

# Write csv
write_csv(output, "data-processed/FullTextScreeningAgreement.csv")
```

**2. Studies with disagreements only**

```{r output disagreements only}
# Filter disagreements only
disagree <- output %>%
  filter(Relevance_Match == FALSE)

# Write csv
write_csv(disagree, "data-processed/FullTextScreeningAgreement_disagreementsOnly.csv")
```

**3. Studies with disagreements only (formatted for SyRF upload)**

```{r output syrf}
# Filter only studies with disagreements from Study Info
syrf <- studyInfo %>%
  filter(Keywords %in% disagree$StudyIdStr) # StudyIdStr is in Keywords column

# Format for SyRF
syrf <- syrf %>%
  rename(Authors = "First Author Surname") %>%
  select(Title, Authors, "Publication Name", "Alternate Name", Abstract, Url, "Author Address", Year, DOI, Keywords, "Reference Type", "PDF Relative Path")

# Write csv
write_csv(syrf, "data-processed/FullTextScreening_forSyRF.csv")
```

The **`r nDifferent` studies** re-uploaded to SyRF can be screened based on full-text by a third reviewer to reconcile disagreements.