---
title: "Full-Text Screening Reconciliation"
author: Emma Wilson
date: "12/11/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r project details, include=FALSE}
projectName <- "Systematic Review and Meta-Analysis of reporting on quality control standards and phenotypes of the basic cell model in brain cancer research: how reproducible is the field?" # Copied and pasted from SyRF
downloadDate <- "12 Nov 2020" # Date data was downloaded from SyRF
```

## Aims

This systematic review project utilised both title/abstract and full-text screening to identify relevant studies. The following code:

1. **Loads** required R packages
2. **Reads in** annotation from SyRF database
3. **Filters** relevant screening question
4. **Compares** Reviewer 1 and Reviewer 2 answers
5. **Outputs** file to reconcile disagreements

## 1. Load R Packages

```{r load libraries, message=FALSE}
library(dplyr)      # Data transformation
library(readr)      # Reads in data
library(tidyr)      # Pivot wider
```

## 2. Read in SyRF Data
Data are study level annotations only, from the SyRF project titled *`r projectName`* downloaded on `r downloadDate`.

```{r read data, message=FALSE}
# Study Level Annotations from SyRF Project
annotations_studyLevel <- read_csv(file = "data-raw/annotations_studyLevel_20201112.csv")
# All Studies from SyRF Project
studyInfo <- read_tsv(file = "data-raw/studyInfo.txt")
```

*Why does `studyInfo` contain data for 1158 studies but only 665 studies are annotated?*
`studyInfo` contains data from all unique studies from the systematic search, including those excluded in the title and abstract screening phase. Only 665 studies were included in title and abstract screening to progress to full text screening then data annotation.

## 3. Tidy Data
Remove irrelevant columns from the dataset and pivot wider to allow each study screening answer to be compared.

```{r tidy data}
# Select Relevant Columns and Rename
annotations_studyLevel <- annotations_studyLevel %>%
  rename(Relevance = "a1baa93f-6871-4806-816e-aad21f550876_Is this article relevant according to inclusion and exclusion criteria?",
         Reason = "05f8cae4-1a23-45d0-a11e-12f99c6afd9c_Why is the study not relevant?",
         Notes = "05f8cae4-1a23-45d0-a11e-12f99c6afd9c_Why is the study not relevant?_Notes") %>%
  select(StudyIdStr, InvestigatorIdStr, Relevance, Reason, Notes)
#Rename InvestigatorIdStr for Convenience
annotations_studyLevel$InvestigatorIdStr <- gsub("a92f6308-5fb6-4754-a80f-5fcead380da6", "Reviewer1", annotations_studyLevel$InvestigatorIdStr)
annotations_studyLevel$InvestigatorIdStr <- gsub("e368d6d0-eeb5-42aa-8aee-4de0c8530da3", "Reviewer2", annotations_studyLevel$InvestigatorIdStr)
# Make Data Wider to Compare
screeningComparison <- annotations_studyLevel %>%
  pivot_wider(names_from = InvestigatorIdStr,
              values_from = c("Relevance", "Reason", "Notes"))
```

## 4. Compare Full-Text Screening Answers
Create a new column to identify studies where two reviewers agreed or disagreed on whether a study was relevant based on full-text screening.

```{r compare}
# Mutate Column Using "ifelse"
screeningComparison <- screeningComparison %>%
  mutate(Relevance_Match = ifelse(Relevance_Reviewer1 == Relevance_Reviewer2, TRUE, FALSE)) %>%
  select(StudyIdStr, Relevance_Reviewer1, Relevance_Reviewer2, Relevance_Match, Reason_Reviewer1, Reason_Reviewer2, Notes_Reviewer1, Notes_Reviewer2) # reorder the columns
```

```{r analyse, include=FALSE}
nTotal <- sum(nrow(screeningComparison)) # Total number of studies
nMatched <- sum(screeningComparison$Relevance_Match == TRUE) # Number of studies matching
nDifferent <- sum(screeningComparison$Relevance_Match == FALSE) # Number of studies with disagreement
```

Out of a **total `r nTotal` studies**, dual screened by two independent reviewers matched on **`r nMatched` studies** and disagreed on **`r nDifferent` studies**.

## 5. Output Disagreements for Reupload to SyRF
Studies reuploaded to SyRF can be screened by a third reviewer to reconcile disagreements.

```{r output syrf}
# Filter only studies with disagreements and merge with studyInfo
syrf <- screeningComparison %>%
  filter(Relevance_Match == FALSE) %>% # Filter only studies with disagreements
  select(StudyIdStr) %>% # StudyIdStr will match with Keywords in studyInfo
  mutate(Keywords = StudyIdStr) %>% # Mutate column named Keywords to allow merge
  merge(studyInfo, by = "Keywords") %>% # Merge
  rename(Authors = "First Author Surname") %>% # Rename for correct parsing into SyRF
  select(Title, Authors, "Publication Name", "Alternate Name", Abstract, Url, "Author Address", Year, DOI, Keywords, "Reference Type", "PDF Relative Path") # Reorder for correct parsing into SyRF

# Write csv
write_csv(syrf, "data-processed/FullTextScreening_forSyRF.csv")
```

The **`r nDifferent` studies** re-uploaded to SyRF can be screened based on full-text by a third reviewer to reconcile disagreements.